### 2014-12-06 Draft/approach.tex
updated formalism

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
\tool\ consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
We next describe each component in detail.

@@

\subsection{Constraint Extractor}
\label{sub:SE}

Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences.
\tool\ uses the formalism proposed by Lo et al.~\cite{lo2009mining} (introduced in Section~\ref{sec:background})
for formalizing the constraints. 
\tool\ extends the operators by proposing two additional operators:

\begin{enumerate}
	\item Forward Prohibition Operator ($\xi_1 \xrightarrow{-} \xi_2$):
	occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$

	\item Backward Prohibition Operator ($\xi_1 \xleftarrow{-} \xi_2$):
	occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
\end{enumerate}

The prohibition operators capture a different class of temporal constraints that cannot be
expressed by the formulae constructed by previously proposed operators and their negations.
For instance, the \textit{prohibition operators} seem to be negation of
\textit{forward eventual operators} and \textit{backward eventual operators}.
However, the negation of forward eventual operators is: not an invocation of $\xi_1$
must be eventually followed by not an invocation of $\xi_2$. In contrast,
\textit{prohibition operators} either negates antecedent or consequent but not both.
In summary, we extended the formalism for temporal rules previously
proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.

\tool\ first identifies $\xi_1$ as the method whose description constraint sentence is part of.
For instance the sentence in Figure~\ref{fig:standep} is part of Delete Bucket method description in \amazonAPI,
$\xi_1$ is instantiated as Delete Bucket method.

\tool\ next identifies $\xi_2$. Since, references to $\xi_2$ may not always be implicit we leverage the semantic graphs. A semantic graph is a representation of concepts of objects and the methods applicable on those objects. Figure~\ref{fig:knowledge} shows a graph for \CodeIn{Object} resource in \amazonAPI.
The phrases in rounded rectangle are the actions applicable on \CodeIn{Object} resource.
Section~\ref{sub:ACA} further describes how these graphs are generated.
\tool\ uses the Algorithm~\ref{alg:SenAnnotaator} to identify $\xi_2$.

@@

\tool\ next identifies the direction (forward or backward) of the relationship by examining the tense of $\xi_2$ reference in the sentence. Past tense is considered as backward and other tenses are considered as forward. For instance, the sentence in Figure~\ref{fig:standep} since ``deleted'' is in past tense and therefore operator is backward and the constraint is 
Delete Object $\xleftarrow{*}$ Delete Method.

>>>>

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
\tool\ consists of following major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
We next describe each component in detail.

@@

\subsection{Constraint Extractor}
\label{sub:ConsExtract}

Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences.

Temporal constraints are expressed as temporal formulae involving: 1) \textit{Predicates} $\xi$ representing method calls and 2) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$. We define following four constraints:

%
%
%To express temporal constraints between two methods $\xi_1,\xi_2$, there two basic constatins 
%
%\tool\ uses the formalism proposed by Lo et al.~\cite{lo2009mining} (introduced in Section~\ref{sec:background})
%for formalizing the constraints. 
%\tool\ extends the operators by proposing two additional operators:

\begin{enumerate}
	\item \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$. 
	\item \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.
	\item \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$
	\item \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$
\end{enumerate}

%The prohibition operators capture a different class of temporal constraints that cannot be
%expressed by the formulae constructed by previously proposed operators and their negations.
%For instance, the \textit{prohibition operators} seem to be negation of
%\textit{forward eventual operators} and \textit{backward eventual operators}.
%However, the negation of forward eventual operators is: not an invocation of $\xi_1$
%must be eventually followed by not an invocation of $\xi_2$. In contrast,
%\textit{prohibition operators} either negates antecedent or consequent but not both.
%In summary, we extended the formalism for temporal rules previously
%proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.

We next show how \tool\ identifies the terms of the constraint formula:

\textbf{$\xi_1$}:
\tool\ first identifies $\xi_1$ as the method whose description constraint sentence is part of.
For instance the sentence in Figure~\ref{fig:standep} is part of Delete Bucket method description in \amazonAPI,
$\xi_1$ is instantiated as Delete Bucket method.

\textbf{$\xi_2$}:
\tool\ next identifies $\xi_2$. Since, references to $\xi_2$ may not always be implicit we leverage the semantic graphs. A semantic graph is a representation of concepts of objects and the methods applicable on those objects. Figure~\ref{fig:knowledge} shows a graph for \CodeIn{Object} resource in \amazonAPI.
The phrases in rounded rectangle are the actions applicable on \CodeIn{Object} resource.
Section~\ref{sub:ACA} further describes how these graphs are generated.
\tool\ uses the Algorithm~\ref{alg:SenAnnotaator} to identify $\xi_2$.

@@

\textbf{Temporal Operator}:
\tool\ next identifies the direction (forward or backward) of the relationship by examining the tense of $\xi_2$ reference in the sentence. Past tense is considered as backward and other tenses are considered as forward. For instance, the sentence in Figure~\ref{fig:standep} since ``deleted'' is in past tense and therefore operator is backward and the constraint is 
Delete Bucket $\leftarrow$ Delete Object.

### 2014-12-06 Draft/background.tex
updated formalism

Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.

>>>>

%Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
%However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
%These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.

### 2014-12-06 Draft/example.tex
updated formalism

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
Customer dissatisfaction, such as the one was caused by this issue with the delete bucket functionality, can lead to a loss in revenue.

>>>>

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed, one of the forum responses recommended the inquisitor to switch to another product.
Customer dissatisfaction caused by such issues with the delete bucket functionality, can lead to a loss in revenue.

### 2014-12-06 Draft/formal.tex
updated formalism

\subsection{Temporal Specifications}
\label{sub:temporal}

We next describe various classes of temporal constraints using formal temporal logic.
Temporal logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}

\textbf{Method Invocation}: 
We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
They define event as \textit{``any concrete or abstract representation of a program state''}. 
We propose the notion of method invocation analogous to the events,
where each method invocation is represented as a tuple which is an ordered set of strings. 
A method invocation is captured as the Tuple \CodeIn{<T> <str1, str2, str3... >}, where \CodeIn{str1, str2, str3}... are string values,
that belong to set of all strings.
The method invocation tuple \CodeIn{<T>} captures information about the return value, enclosing type, name, and the parameter types of the method.
Therefore a tuple \CodeIn{<T> <String, Bar, foo, Integer, Integer>} represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}

\textbf{Method Invocation Predicates}: We define method predicate as a predicate $E$ over method invocations.
We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method predicate $\xi$.
In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
The predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}. The simplest form of these predicates is of type \CodeIn{\$2 = sym} which refer to method invocations of name \CodeIn{sym}.

\textbf{Temporal Operators}: Temporal constraints~\footnote{Temporal formulae} are constructed by combining method invocation predicates using temporal operators. Lo et al.~\cite{lo2009mining}, proposed the following temporal operators:

\begin{enumerate}

\item \textit{Forward Eventual Operator ($\xi_1 \xrightarrow{*} \xi_2$)}:
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$

\item \textit{Backward Eventual Operator: ($\xi_1 \xleftarrow{*} \xi_2$)}:
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$

\item \textit{Forward Alternation Operator ($\xi_1 \xrightarrow{a} \xi_2$)}:
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between

\item \textit{Backward Alternation Operator ($\xi_1 \xleftarrow{a} \xi_2$)}:
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
\end{enumerate}

\textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation. Formal representation of temporal constraints are obtained by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed. For instance, consider the constraint any method in an enclosing type \CodeIn{Obj} must not be invoked after method \CodeIn{foo} in the \CodeIn{Obj}: $\forall$ \CodeIn{m <m in Obj> !=<foo in Obj>}.

>>>>

%\subsection{Temporal Specifications}
%\label{sub:temporal}
%
%We next describe various classes of temporal constraints using formal temporal logic.
%Temporal logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
%We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}
%
%\textbf{Method Invocation}: 
%We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
%They define event as \textit{``any concrete or abstract representation of a program state''}. 
%We propose the notion of method invocation analogous to the events,
%where each method invocation is represented as a tuple which is an ordered set of strings. 
%A method invocation is captured as the Tuple \CodeIn{<T> <str1, str2, str3... >}, where \CodeIn{str1, str2, str3}... are string values,
%that belong to set of all strings.
%The method invocation tuple \CodeIn{<T>} captures information about the return value, enclosing type, name, and the parameter types of the method.
%Therefore a tuple \CodeIn{<T> <String, Bar, foo, Integer, Integer>} represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
%that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
%For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}
%
%
%\textbf{Method Invocation Predicates}: We define method predicate as a predicate $E$ over method invocations.
%We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method predicate $\xi$.
%In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
%The predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}. The simplest form of these predicates is of type \CodeIn{\$2 = sym} which refer to method invocations of name \CodeIn{sym}.
%
%\textbf{Temporal Operators}: Temporal constraints~\footnote{Temporal formulae} are constructed by combining method invocation predicates using temporal operators. Lo et al.~\cite{lo2009mining}, proposed the following temporal operators:   
%
%\begin{enumerate}
%
%\item \textit{Forward Eventual Operator ($\xi_1 \xrightarrow{*} \xi_2$)}:
%occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$
%
%\item \textit{Backward Eventual Operator: ($\xi_1 \xleftarrow{*} \xi_2$)}:
%occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$
%
%\item \textit{Forward Alternation Operator ($\xi_1 \xrightarrow{a} \xi_2$)}:
%occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
%
%\item \textit{Backward Alternation Operator ($\xi_1 \xleftarrow{a} \xi_2$)}:
%occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
%\end{enumerate}
%
%\textbf{Quantification}: Quantification is used to introduce constraints involving parameter and return types of a method invocation. Formal representation of temporal constraints are obtained by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed. For instance, consider the constraint any method in an enclosing type \CodeIn{Obj} must not be invoked after method \CodeIn{foo} in the \CodeIn{Obj}: $\forall$ \CodeIn{m <m in Obj> !=<foo in Obj>}.

### 2014-12-06 Draft/introduction.tex
updated formalism

Application Programming Interface (API) has evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, APIs (whether traditional or web-based) have some rules or constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.

@@

To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
We propose to employ ML as a means to identify temporal constraint sentences from rest and then use NLP techniques to infer formal constraints from identified sentences. 
Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
our approach addresses two major challenges to automatically infer specifications from natural language text in API documents

First, classifying temporal constraint sentences is difficult. A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting an exponential number of keywords. To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.

@@

In summary, our \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
This paper makes the following main contributions:

>>>>

Application Programming Interfaces (APIs) have evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, APIs (whether traditional or web-based) have some rules or constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.

@@

To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal constraints from the identified sentences. 
Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
our approach addresses two major challenges to automatically infer specifications from natural language text in API documents

First, classifying temporal constraint sentences is difficult. A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting an large number of keywords.
Furthermore, keywords often have confounding effects that inversely affects accuracy.
To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.

@@

In summary, \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
This paper makes the following main contributions:

### 2014-12-06 Draft/related.tex
updated formalism

Additionally, contracts are typically in the form of assertions on the state (member variables/ properties) of a program. In contrast, temporal constraints specify the ordering of method invocations and therefore are different.
Furthermore, since \tool\ infers temporal constraint from API documents, we believe \tool\ can work in conjunction with existing approaches
to infer a comprehensive set of program specifications.

@@

\textbf{NLP in SE}:
NLP techniques are being increasingly applied in the SE domain. 
Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
They rely on predefined rule templates targeted towards threading and lock related comments, and then apply ML-based approach to find comments following such rules.
The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
In comparison, the temporal constraints inferred by \tool\ are the restriction imposed by the API library being used by the client code.

>>>>

Additionally, contracts are typically in the form of assertions on the state (member variables/ properties) of a program. In contrast, temporal constraints specify the ordering of method invocations and therefore are different.
Furthermore, since \tool\ infers temporal constraint from API documents, we envision \tool\ to work in conjunction with existing approaches
to infer a comprehensive set of program specifications.

@@

\textbf{NLP in Software Engineering (SE)}:

Research advances~\cite{Marneffe08COLING,KleinNIPS03} in the accuracy of existing NLP techniques have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain. 
Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
They rely on predefined rule templates targeted towards threading and lock related comments, and then apply ML-based approach to find comments following such rules.
The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
In comparison, the temporal constraints inferred by \tool\ are the restriction imposed by the API library being used by the client code.
